---
title: "Access to Restorative Reproductive Medicine Practices by Caller Identity and Service Menu: A National Secret-Shopper Audit"
author: "Sofie Rosenberg, MD; Melanie Mandell, MPH; Elizabeth Steiner, MD; Samuel Raine, MD; Tyler M. Muffly, MD"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: false
    df_print: kable
  word_document:
    toc: true
    toc_depth: 3
---

```{css, echo=FALSE}
/* Obstetrics & Gynecology (The Green Journal) Custom Styling */
body {
  font-family: Arial, Helvetica, sans-serif;
  font-size: 12pt;
  line-height: 1.6;
  color: #111111;
  background-color: #ffffff;
  padding: 20px;
}

.main-container {
  max-width: 1140px !important;
  margin: 0 auto !important;
}

/* Fix floating Table of Contents overlap */
div.tocify {
  width: 230px !important;
  max-width: 230px !important;
  font-family: Arial, Helvetica, sans-serif !important;
  font-size: 11pt !important;
  border: 1px solid #e2e8f0 !important;
  border-radius: 6px !important;
  background-color: #f8fafc !important;
  box-shadow: 0 1px 3px rgba(0,0,0,0.05) !important;
}

div.tocify .tocify-header {
  font-weight: 600 !important;
  color: #003366 !important;
}

div.tocify ul, div.tocify li {
  line-height: 1.35 !important;
}

.tocify-subheader .tocify-item {
  font-size: 10pt !important;
  padding-left: 15px !important;
}

@media (min-width: 992px) {
  .col-md-9 {
    padding-left: 35px !important;
  }
}

h1, h2, h3, h4 {
  font-family: Arial, Helvetica, sans-serif;
  color: #003366; /* Deep ACOG Navy */
  font-weight: 700;
}

h1.title {
  font-size: 22pt;
  color: #003366;
  border-bottom: 3px solid #003366;
  padding-bottom: 8px;
  margin-bottom: 4px;
}

h2 {
  font-size: 14pt;
  text-transform: uppercase;
  letter-spacing: 0.8px;
  border-bottom: 1px solid #c8d6e5;
  padding-bottom: 4px;
  margin-top: 28px;
}

h3 {
  font-size: 12pt;
  color: #2c3e50;
  margin-top: 18px;
}

.precis-box {
  background-color: #f4f7fa;
  border-left: 5px solid #003366;
  padding: 14px 18px;
  margin: 20px 0 25px 0;
  font-family: Arial, Helvetica, sans-serif;
  font-size: 11pt;
}

.precis-title {
  font-weight: bold;
  color: #003366;
  text-transform: uppercase;
  letter-spacing: 0.5px;
  margin-bottom: 4px;
}

.journal-header {
  background-color: #003366;
  color: #ffffff;
  padding: 8px 14px;
  font-family: Arial, Helvetica, sans-serif;
  font-size: 11pt;
  font-weight: bold;
  letter-spacing: 1px;
  text-transform: uppercase;
  margin-bottom: 15px;
  display: flex;
  justify-content: space-between;
}

.meta-block {
  font-family: Arial, Helvetica, sans-serif;
  font-size: 11pt;
  color: #444444;
  margin-bottom: 25px;
  line-height: 1.5;
}

table {
  border-collapse: collapse;
  width: 100%;
  margin: 20px 0;
  font-size: 11pt;
  font-family: Arial, Helvetica, sans-serif;
}

th {
  background-color: #003366;
  color: white;
  padding: 9px 12px;
  text-align: left;
  font-weight: 600;
}

td {
  padding: 8px 12px;
  border-bottom: 1px solid #e1e8ed;
}

tr:nth-child(even) {
  background-color: #f8fafc;
}

.alert-callout {
  background-color: #fff9e6;
  border-left: 4px solid #f39c12;
  padding: 12px 16px;
  margin: 18px 0;
  font-size: 11pt;
}

code {
  background-color: #f1f5f9;
  padding: 2px 5px;
  border-radius: 3px;
  font-family: monospace;
  font-size: 11pt;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
suppressMessages({library(dplyr); library(knitr); library(lme4); library(mysterycall)})

OUT <- "mysterycall_outputs"
rd  <- function(f) read.csv(file.path(OUT, f), stringsAsFactors = FALSE)

d    <- rd("labubu_cleaned_analysis.csv")
mc   <- rd("mysterycall_paired_acceptance_mcnemar.csv")     # paired OFFER
mcr  <- rd("mysterycall_paired_reached_mcnemar.csv")        # paired REACHABILITY
cov  <- rd("practice_scenario_coverage.csv")
casc <- rd("mysterycall_access_cascade_by_scenario.csv")
cdom <- rd("caller_dominance_by_scenario.csv")
crat <- rd("caller_rates.csv")
wide <- rd("matched_acceptance_wide.csv")

tf <- function(x) x %in% c(TRUE, "TRUE", "True", 1, "1")
d$scenario <- factor(d$scenario, levels = c("Straight couple", "Lesbian couple", "Single mother"))
d$appt_offered <- suppressWarnings(as.integer(d$appt_offered))
d$appt_offered_broad <- suppressWarnings(as.integer(d$appt_offered_broad))

inc  <- d[tf(d$analytic_inclusion), ]                     # reached staff, asked the service items
rch  <- d[tf(d$reached), ]                                # a live office answered
oa   <- d[tf(d$in_offer_den) & !is.na(d$appt_offered) & !is.na(d$scenario), ]
wsub <- d |> filter(tf(analytic_inclusion), !is.na(business_days), business_days >= 0)

# ── Formatting helpers, all package-backed so nothing is hand-typed ───────────
# Wilson CI for a single proportion, via mysterycall_prevalence_ci().
pci <- function(data, var, digits = 1) {
  tb <- as.data.frame(mysterycall_prevalence_ci(data, var = var))
  r  <- tb[tb$category %in% c("TRUE", "1"), ][1, ]
  if (nrow(r) == 0 || is.na(r$proportion))
    return(sprintf("0.0%% (0/%d)", nrow(data)))
  sprintf("%.*f%% (95%% CI %.*f-%.*f%%; %d/%d)",
          digits, 100 * r$proportion, digits, 100 * r$ci_lower,
          digits, 100 * r$ci_upper, r$n, r$total)
}
svc <- function(v) pci(inc, v)

# ── Manuscript claims ─────────────────────────────────────────────────────────
# Headline numbers are looked up by claim id from the generated claims table,
# not recomputed here. Two scripts computing "the offer rate" over different
# denominators is the failure this prevents: a claim either resolves to a row
# in manuscript_claims.csv or the render stops.
claims_path <- file.path(OUT, "manuscript_claims.csv")
claims <- if (file.exists(claims_path)) rd("manuscript_claims.csv") else NULL

claim <- function(id, field = "estimate") {
  if (is.null(claims)) stop("manuscript_claims.csv is absent; run ",
                            ".github/scripts/manuscript-claims.R")
  row <- claims[claims$claim_id == id, ]
  if (!nrow(row)) stop("no such manuscript claim: ", id)
  row[[field]][1]
}
claim_pct <- function(id, digits = 1) sprintf(paste0("%.", digits, "f%%"), claim(id))

N_REC   <- nrow(d); N_PRAC <- dplyr::n_distinct(d$practice_id)
N_RCH   <- nrow(rch); N_INC <- nrow(inc); N_OFFER <- nrow(oa); N_WAIT <- nrow(wsub)
N_TRIAD <- sum(cov$n_scenarios == 3)
N_DECL  <- sum(tf(d$reached) & !tf(d$analytic_inclusion))

# ── Primary model: appointment offered, complete practice triads ──────────────
triad_ids <- cov$practice_id[cov$n_scenarios == 3]
oa_triad  <- oa[oa$practice_id %in% triad_ids & !is.na(oa$practice_id), ]
oa_triad$scenario <- droplevels(factor(oa_triad$scenario,
                     levels = c("Straight couple", "Lesbian couple", "Single mother")))

fit_offer_triad <- tryCatch(
  mysterycall_logistic_model(oa_triad, outcome = "appt_offered",
                             predictors = "scenario", random_intercept = "practice_id"),
  error = function(e) NULL)

fit_offer_broad <- tryCatch(
  mysterycall_logistic_model(
    d[tf(d$in_offer_den) & !is.na(d$appt_offered_broad) & !is.na(d$scenario) &
      !is.na(d$practice_id), ],
    outcome = "appt_offered_broad", predictors = "scenario",
    random_intercept = "practice_id"),
  error = function(e) NULL)

# OR (95% CI), p — generated from the fit, never typed in.
AB <- function(fit, term, what = c("or_ci", "or_p")) {
  what <- match.arg(what)
  if (is.null(fit)) return("not estimable")
  a <- tryCatch(mysterycall_abstract_numbers(logistic_fit = fit, exposure_term = term),
                error = function(e) NULL)
  if (is.null(a)) return("not estimable")
  as.character(a[[what]])
}
orci <- function(fit, term) AB(fit, term, "or_ci")
orp  <- function(fit, term) AB(fit, term, "or_p")

# Paired proportion differences with 95% CIs (offer outcome).
paired_diff_ci <- function(col_a, col_b) {
  ok <- !is.na(wide[[col_a]]) & !is.na(wide[[col_b]])
  a <- tf(wide[[col_a]][ok]); b <- tf(wide[[col_b]][ok])
  n <- length(a)
  if (n == 0) return("no paired practices")
  diff <- mean(a) - mean(b)
  f10 <- sum(a & !b); f01 <- sum(!a & b)
  se <- sqrt((f10 + f01 - (f10 - f01)^2 / n) / n^2)
  sprintf("%+.1f percentage points (95%% CI %+.1f to %+.1f; n = %d practices)",
          100 * diff, 100 * (diff - 1.96 * se), 100 * (diff + 1.96 * se), n)
}

# Wait time: the package log-transforms, so report geometric mean ratios.
fit_wait <- tryCatch(
  mysterycall_lmm(d[!is.na(d$business_days) & !is.na(d$practice_id) & !is.na(d$scenario), ],
                  outcome = "business_days", predictors = "scenario",
                  random_intercept = "practice_id"),
  error = function(e) NULL)
gmr <- function(term, what = c("est", "ci")) {
  what <- match.arg(what)
  if (is.null(fit_wait) || is.null(fit_wait$gmr_table)) return("not estimable")
  g <- as.data.frame(fit_wait$gmr_table); r <- g[g$term == term, ][1, ]
  if (nrow(r) == 0 || is.na(r$GMR)) return("not estimable")
  if (what == "est") sprintf("%.2f", r$GMR)
  else sprintf("%.2f (95%% CI %.2f-%.2f)", r$GMR, r$GMR_lo, r$GMR_hi)
}

# Median (IQR) business-day wait by scenario, computed not typed.
wait_med <- function(s) {
  x <- wsub$business_days[wsub$scenario == s]
  if (!length(x)) return("no observations")
  sprintf("%.0f business days (IQR %.0f-%.0f; n = %d)",
          median(x), quantile(x, .25), quantile(x, .75), length(x))
}

conc_range <- sprintf("%.0f%%-%.0f%%",
                      100 * min(mcr$concordant / mcr$n_paired),
                      100 * max(mcr$concordant / mcr$n_paired))
mde_range  <- sprintf("OR %.1f to OR %.1f", min(mc$mde_or_80power, na.rm = TRUE),
                      max(mc$mde_or_80power, na.rm = TRUE))
cram <- tryCatch(round(mysterycall_test_categorical(
          d[!is.na(d$scenario), ], row_var = "caller", col_var = "scenario")$cramers_v, 2),
        error = function(e) NA)
```

<div class="journal-header">
  <span>Obstetrics &amp; Gynecology</span>
  <span>Original Research</span>
</div>

<div class="meta-block">
  Authors: Sofie Rosenberg, MD; Melanie Mandell, MPH; Elizabeth Steiner, MD; Samuel Raine, MD; Tyler M. Muffly, MD<br>
  Affiliation: Department of Obstetrics and Gynecology, Denver Health and Hospital Authority, University of Colorado School of Medicine, Denver, Colorado<br>
  Institutional Review Board: COMIRB 25-2596 (Approved)<br>
  Financial Disclosure: The authors report no conflicts of interest or relevant financial disclosures<br>
  Data Audit &amp; Provenance: Automatically compiled from active dataset LABUBU_DATA_LABELS_2026-08-11_2017.csv (`r N_REC` calls across `r N_PRAC` practices)
</div>

<div class="precis-box">
  <div class="precis-title">Pr&eacute;cis</div>
  Restorative Reproductive Medicine practices almost uniformly offer cycle tracking but rarely offer intrauterine insemination, in vitro fertilization, or donor sperm services, with high baseline practice scheduling concordance across caller identities.
</div>

## ABSTRACT

OBJECTIVE: To characterize reproductive health services offered by Restorative Reproductive Medicine (RRM) practices in the United States and to examine whether appointment access differs by caller family structure.

METHODS: In a national mystery-caller (secret shopper) audit, RRM practices were telephoned by trained callers presenting one of three standardized clinical scenarios: a straight couple, a lesbian couple, or a single mother seeking donor sperm care. Each practice was eligible for one call per scenario. Because the data-collection instrument contained no explicit "was an appointment offered" item, the offer outcome was derived: a call was scored as offered when a first-available appointment date was recorded, and as not offered when the practice stated it was not accepting new patients; a sensitivity definition additionally counted a concrete scheduling timeframe as an offer. Reaching a live office and being offered an appointment were analyzed as separate cascade stages. Mixed-effects logistic regression with a practice random intercept was fitted to complete practice triads; within-practice matched contrasts used exact McNemar tests with minimum detectable effect (MDE) specifications.

RESULTS: `r N_REC` calls were placed to `r N_PRAC` practices. A live office was reached on `r pci(d, "reached")` of calls; `r N_OFFER` calls were eligible for the offer analysis and `r N_TRIAD` practices completed all three scenarios. Among calls reaching staff (N = `r N_INC`), cycle tracking was offered by `r svc("service_cycle_tracking")`, ovulation induction by `r svc("service_ovulation_induction")`, intrauterine insemination (IUI) by `r svc("service_iui")`, in vitro fertilization (IVF) by `r svc("service_ivf")`, and donor sperm care by `r svc("donor_sperm_yes")`. Appointment-offer rates were `r claim_pct("offer_straight")` for straight couples, `r claim_pct("offer_lesbian")` for lesbian couples, and `r claim_pct("offer_single_mother")` for single mothers. In complete-triad mixed-effects logistic regression, relative to straight couples, the odds of an appointment offer were OR `r orci(fit_offer_triad, "scenarioLesbian couple")` for lesbian couples (p = `r orp(fit_offer_triad, "scenarioLesbian couple")`) and OR `r orci(fit_offer_triad, "scenarioSingle mother")` for single mothers (p = `r orp(fit_offer_triad, "scenarioSingle mother")`). Under the broader offer definition these attenuated to OR `r orci(fit_offer_broad, "scenarioLesbian couple")` and OR `r orci(fit_offer_broad, "scenarioSingle mother")` respectively. Caller identity was strongly associated with scenario (Cramér's V = `r cram`), so scenario and caller effects are not separately identifiable.

CONCLUSION: RRM practices uniformly provide cycle tracking but rarely provide IUI, IVF, or donor sperm care, a structural service limitation for single mothers and same-sex couples that does not depend on staff attitudes. Apparent differences in appointment offers by caller identity were sensitive to the outcome definition and confounded with caller assignment, and should be regarded as hypothesis-generating.

---

## INTRODUCTION

Restorative Reproductive Medicine (RRM) is an approach to reproductive healthcare that emphasizes diagnosing and treating underlying physiological causes of subfertility rather than utilizing assisted reproductive technology (ART) such as in vitro fertilization (IVF).[1,2] Because RRM clinical frameworks explicitly omit interventions like IVF or intrauterine insemination (IUI), prospective patients may encounter service menus that differ substantially from conventional fertility clinics. Furthermore, access to these specialized practices may vary depending on patient family structure, particularly for patients requiring donor gametes or non-traditional family building.[8,9]

Mystery-caller (audit) methodology employs standardized simulated callers to objectively evaluate real-world access to healthcare while eliminating social desirability bias.[3-7] Prior healthcare audit studies in obstetrics, gynecology, and primary care have documented significant disparities in appointment access based on insurance coverage, socioeconomic status, and demographic characteristics.[3-6] However, national audit data regarding service availability and scheduling access across RRM practices remain unstudied in the peer-reviewed literature.

This national secret-shopper audit had two objectives: (1) to define the scope of reproductive services offered by RRM practices, and (2) to explore whether practice willingness to schedule an appointment differs by caller family structure (straight couple, lesbian couple, single mother using donor sperm).

---

## SOURCES AND METHODS

### Study Design and Practice Eligibility
We conducted a national within-practice audit study of RRM practices in the United States between 2025 and 2026. A comprehensive national roster of RRM practices was compiled from professional directories and clinical registries. The study protocol was reviewed and approved by the Colorado Multiple Institutional Review Board (COMIRB 25-2596).

Trained callers telephoned each eligible practice during standard business hours (08:00–17:00 local time, excluding 12:00–13:00). Each practice was assigned to receive one telephone call for each of three clinical scenarios. Because each practice served as its own control across scenarios, practice identity was treated as a random intercept in all statistical models.

### Standardized Caller Scenarios
Three standardized clinical scenarios were designed:

- Straight Couple: A female caller seeking fertility evaluation with a male partner.
- Lesbian Couple: A female caller seeking fertility evaluation with a female partner.
- Single Mother: A single female caller seeking fertility evaluation using donor sperm.

Call scripts were strictly standardized across scenarios, differing only in the caller's stated partner status and clinical inquiry regarding donor sperm care.

### Outcome Definitions
Call dispositions were mapped to the standard access-audit exclusion codes, which distinguish three nested constructs that are frequently conflated: whether a live office was **reached**, whether the call was **eligible** for the offer analysis, and whether an appointment was **offered**.

- **Reached a live office**: staff engaged with the caller (including calls that ended in a stated refusal or an extended hold). Voicemail, wrong numbers, unanswered lines, personal phones, and closed systems were not reached.
- **Appointment offered (primary, strict)**: among offer-eligible calls, a first-available appointment date was recorded. A stated "not accepting new patients" was scored as not offered.
- **Appointment offered (sensitivity, broad)**: as above, but a concrete scheduling timeframe reported by staff without a specific date was also counted as an offer.

The data-collection instrument did not contain an explicit item asking whether staff agreed to schedule the caller. The offer outcome is therefore a derived proxy, and this is the study's principal measurement limitation (see Limitations). Wait time was the number of business days (Monday–Friday, excluding US federal holidays) between the call and the first available appointment, with same-day appointments retained as a wait of zero.

### Statistical Analysis and Power
Proportions carry 95% Wilson score confidence intervals.[13,14] The access cascade reports each stage with its own denominator, nested within the preceding stage.

Mixed-effects logistic regression with a practice random intercept was fitted to the offer outcome, first on the subset of complete practice triads (N = `r N_TRIAD` practices) to remove practice-selection dialing bias, then on the full offer sample, and finally under the broad offer definition as a sensitivity analysis. Because the appointment date was missing for a scenario-dependent share of calls, a two-part hurdle model estimated the obtainment and wait-given-obtainment steps jointly rather than conditioning on complete cases. Wait time was additionally modeled with a linear mixed model; because the wait distribution is right-skewed, the outcome was log-transformed and estimates are reported as back-transformed geometric mean ratios (GMR), not as differences in days.

Within-practice matched contrasts used exact McNemar tests. Power in paired audit designs is governed by the number of discordant practices, which here was small; minimum detectable effect (MDE) odds ratios at 80% power (α = 0.05) ranged from `r mde_range` and are reported alongside every paired contrast. In accordance with SAMPL reporting guidelines,[14] point estimates are presented with 95% confidence intervals to establish precision limits rather than relying on underpowered null hypothesis significance tests. All analyses were conducted in R version 4.4.2 using the `mysterycall` package.

---

## RESULTS

### Access Cascade
A total of `r N_REC` telephone calls were placed to `r N_PRAC` unique RRM practices. A live office was reached on `r N_RCH` calls (`r pci(d, "reached")`). Of these, `r N_DECL` reached calls ended in a stated refusal or extended hold, and `r N_INC` proceeded to the full interview. `r N_TRIAD` practices completed all three scenario calls (complete triads), `r sum(cov$n_scenarios == 2)` completed two, and `r sum(cov$n_scenarios == 1)` completed one.

```{r strobe, fig.cap="Figure 1. STROBE flow diagram. Reaching a live office and being offered an appointment are separate stages with separate denominators.", out.width="85%", fig.align="center"}
strobe_png <- file.path(OUT, "figures", "fig0_strobe_flow.png")
if (file.exists(strobe_png)) knitr::include_graphics(strobe_png)
```

```{r Table1}
t1 <- casc |>
  transmute(
    Scenario                       = scenario,
    `Calls placed`                 = calls_placed,
    `Reached live office`          = reached,
    `Offer-eligible`               = offer_eligible,
    `Offered (strict)`             = sprintf("%d (%.1f%%)", offered_strict, pct_offered_strict),
    `Offered (broad)`              = sprintf("%d (%.1f%%)", offered_broad,  pct_offered_broad)
  )
kable(t1, caption = "Table 1. Access cascade by caller scenario. Each stage is nested within the preceding one.")
```

### Reproductive Services Offered
Among calls that reached staff and completed the service interview (N = `r N_INC`), RRM practices almost uniformly offered natural cycle tracking but rarely provided ART or donor gamete services (Table 2).

```{r Table2}
t2 <- data.frame(
  `Reproductive Service` = c(
    "Cycle tracking", "Hormonal labs / fertility timing", "Ovulation induction",
    "Intrauterine insemination (IUI)", "In vitro fertilization (IVF)",
    "Works with donor sperm"),
  `Proportion Offered (95% CI)` = c(
    svc("service_cycle_tracking"), svc("service_hormonal_timing"),
    svc("service_ovulation_induction"), svc("service_iui"),
    svc("service_ivf"), svc("donor_sperm_yes")),
  check.names = FALSE)
kable(t2, caption = sprintf("Table 2. Reproductive healthcare services offered by RRM practices (N = %d calls reaching staff)", N_INC))
```

Cycle tracking was offered in `r svc("service_cycle_tracking")` of encounters. In contrast, IUI was offered in `r svc("service_iui")`, IVF in `r svc("service_ivf")`, and donor sperm management in `r svc("donor_sperm_yes")`. The IUI and IVF counts each reflect a single practice and should be read as an upper bound on availability rather than a stable rate estimate.

### Appointment Offers by Caller Identity
Appointment-offer rates among offer-eligible calls were `r claim_pct("offer_straight")` for straight couples, `r claim_pct("offer_lesbian")` for lesbian couples, and `r claim_pct("offer_single_mother")` for single mothers (Table 1).

In complete-triad mixed-effects logistic regression (N = `r N_TRIAD` practices), relative to straight-couple callers, the odds of an appointment offer were OR `r orci(fit_offer_triad, "scenarioLesbian couple")` for lesbian couples (p = `r orp(fit_offer_triad, "scenarioLesbian couple")`) and OR `r orci(fit_offer_triad, "scenarioSingle mother")` for single mothers (p = `r orp(fit_offer_triad, "scenarioSingle mother")`). The confidence intervals span orders of magnitude, reflecting near-separation at this sample size; direction is interpretable, magnitude is not.

Under the broad offer definition, which additionally credits a stated scheduling timeframe, the same contrasts attenuated to OR `r orci(fit_offer_broad, "scenarioLesbian couple")` and OR `r orci(fit_offer_broad, "scenarioSingle mother")`. The dependence of the estimate on the outcome definition is material and is discussed below.

```{r Table3}
t3 <- mc |>
  transmute(
    `Paired Comparison`    = contrast,
    `Paired Practices (n)` = n_paired,
    `Concordant`           = concordant,
    `Discordant`           = discordant,
    `Exact McNemar P`      = sprintf("%.3f", mcnemar_p),
    `MDE (80% Power)`      = sprintf("OR %.1f", mde_or_80power))
kable(t3, caption = "Table 3. Within-practice matched paired appointment-offer analysis. Only discordant practices contribute information.")
```

Within-practice paired differences in offer rate were: Straight vs Single Mother `r paired_diff_ci("Straight_couple", "Single_mother")`; Lesbian vs Single Mother `r paired_diff_ci("Lesbian_couple", "Single_mother")`; Straight vs Lesbian `r paired_diff_ci("Straight_couple", "Lesbian_couple")`. Practices treated callers identically in `r conc_range` of paired reachability comparisons.

### Caller Assignment
Scenarios were not randomized across callers (Table 4). Caller identity was strongly associated with scenario (Cramér's V = `r cram`), and per-caller offer rates varied widely. Consequently, a scenario contrast and a caller contrast are numerically the same comparison, and within-practice pairing does not separate them because the paired calls were placed by different callers.

```{r Table4}
t4 <- cdom |>
  transmute(
    Scenario                    = scenario,
    `Calls placed`              = n_calls,
    `Largest single caller`     = top_caller,
    `Their share of the arm`    = sprintf("%d (%.1f%%)", top_caller_n, top_caller_pct))
kable(t4, caption = "Table 4. Concentration of each scenario arm in a single caller.")
```

### Wait Time to First Available Appointment
Among calls with an observed appointment date (N = `r N_WAIT`), the median wait was `r wait_med("Straight couple")` for straight couples, `r wait_med("Lesbian couple")` for lesbian couples, and `r wait_med("Single mother")` for single mothers. In the log-transformed mixed model, waits relative to straight-couple callers had a geometric mean ratio of `r gmr("scenarioLesbian couple", "ci")` for lesbian couples and `r gmr("scenarioSingle mother", "ci")` for single mothers; a ratio below 1.00 indicates a shorter wait. Because appointment dates are missing for a scenario-dependent share of calls, these complete-case estimates condition on having been offered an appointment and are reported as descriptive.

---

## DISCUSSION

### Principal Findings
This national secret-shopper audit produced one well-powered finding and one hypothesis-generating signal.

The well-powered finding is structural. RRM practice service menus almost universally include cycle tracking (`r svc("service_cycle_tracking")`) while rarely including IUI (`r svc("service_iui")`), IVF (`r svc("service_ivf")`), or donor sperm care (`r svc("donor_sperm_yes")`). For single mothers and same-sex female couples, whose path to pregnancy clinically requires donor sperm or IUI/IVF, the absence of these services is a barrier to care that operates independently of any staff attitude or scheduling decision.[9-12] This result rests on directly observed service responses, not on a derived outcome, and is unaffected by how calls were assigned to callers.

The hypothesis-generating signal is that appointment-offer rates differed across caller scenarios in the observed direction of disadvantage for lesbian couples and single mothers. We do not present this as an established effect, for the reasons below.

### Why the Offer Difference Is Not Yet a Finding
Three features of the design prevent a causal reading.

First, the outcome is a proxy. The instrument recorded no explicit "did the practice agree to schedule you?" item, so an offer had to be inferred from whether an appointment date was written down. A call in which staff offered an appointment that the caller did not date is scored as a refusal. When the definition is broadened to credit a concrete scheduling timeframe, the contrasts attenuate substantially (OR `r orci(fit_offer_triad, "scenarioLesbian couple")` to OR `r orci(fit_offer_broad, "scenarioLesbian couple")` for lesbian couples). An effect that moves this much with the coding rule is not yet separable from a documentation artifact.

Second, caller and scenario are confounded. Callers were not randomized across scenarios; each arm was dominated by a small number of callers (Table 4; Cramér's V = `r cram`), and per-caller offer rates ranged widely. Because the paired within-practice design compares scenarios that were dialed by different people, matching removes practice-level confounding but not caller-level confounding. In a model adjusting for caller, the scenario standard errors inflate to the point of non-identifiability, which is itself the evidence that the two cannot be separated in these data.

Third, the matched analysis is underpowered. Discordant practices number `r paste(mc$discordant, collapse = ", ")` across the three contrasts, giving minimum detectable effects of `r mde_range` at 80% power. Plausible audit-study effects are well below this floor.

### Methodological Implications for Audit Studies
Two design lessons generalize.[3,7] Reaching a live office and being offered an appointment are distinct constructs with different denominators; collapsing them into a single "acceptance" variable makes the analytic inclusion criterion and the outcome the same measurement, which forces acceptance to 100% within the analytic sample and discards stated refusals — the only unambiguous negative outcomes. Reporting the cascade stage by stage avoids this. Separately, an audit design that assigns caller identity non-randomly across the very conditions it means to contrast cannot recover the contrast, regardless of how sophisticated the within-unit matching is; caller assignment should be randomized or blocked at design time.

### Strengths and Limitations
Strengths include the national scope, the within-practice design, business-day calendar modeling, and explicit cascade reporting with stage-specific denominators.

Limitations:

1. **The offer outcome is derived, not measured.** No instrument item recorded whether staff agreed to schedule the caller. Results are sensitive to the coding rule, as shown by the strict versus broad comparison.
2. **Caller is confounded with scenario.** Scenario arms were dominated by different callers, and caller-level offer rates vary widely. Scenario effects cannot be distinguished from caller effects.
3. **Limited statistical power for matched contrasts.** With `r paste(mc$discordant, collapse = ", ")` discordant practices, only very large effects (`r mde_range`) are detectable.
4. **Informative missingness.** Appointment dates are absent for a scenario-dependent share of calls; complete-case wait-time results condition on having been offered an appointment and do not generalize to all callers.
5. **Reachability is low.** A live office was reached on `r pci(d, "reached")` of calls, so all interview-based results describe the reachable subset of practices.
6. **Single call per scenario.** Day-to-day and staff-to-staff variation within practices could not be separately evaluated.

### Recommendations for the Next Wave
Adding an explicit appointment-offer item to the data-collection instrument, and randomizing or blocking caller assignment across scenarios, would convert the exploratory contrast reported here into an estimable effect. The three "restrictions on the individuals you would provide care to" checkboxes already in the instrument are the only directly measured discrimination item; their coding is currently ambiguous and should be adjudicated against the codebook before use.

### Conclusion
Restorative Reproductive Medicine practices in the United States uniformly provide natural cycle tracking but rarely offer IUI, IVF, or donor sperm management, a structural limitation for patients who require donor gametes. Observed differences in appointment offers by caller family structure were sensitive to outcome definition and confounded with caller assignment, and require a randomized-caller design with an explicit offer measure to evaluate.

---

## REFERENCES

1. Stanford JB, Parnell TA, Boyle PC. Restorative reproductive medicine: an overview. Curr Med Res Opin. 2012;28(9):1451-1463.
2. Tham E, Schliep K, Stanford J. Natural procreative technology for infertility and recurrent miscarriage. Can Fam Physician. 2012;58(5):e267-e274.
3. Kugelmass H. "Sorry, I'm Not Accepting New Patients": An Audit Study of Access to Mental Health Care. J Health Soc Behav. 2016;57(2):168-183.
4. Kugelmass H. Disability, Social Class, and Racial Disparities in Access to Mental Health Care: An Audit Study. J Health Soc Behav. 2019;60(4):460-476.
5. Bisgaier J, Rhodes KV. Auditing access to specialty care for children with public insurance. N Engl J Med. 2011;364(24):2326-2333.
6. Rhodes KV, Kenney GM, Wissoker D, et al. Primary care access for new patients on Medicaid. Ann Intern Med. 2014;160(12):813-820.
7. Gross CP, Andersen MS, Krumholz HM. Audit studies in health services research. JAMA. 2019;322(3):205-207.
8. Lauster N, Easterbrook A. No couples allowed: Housing discrimination against same-sex couples in Vancouver. Can Stud Popul. 2011;38(3-4):57-75.
9. Practice Committee of the American Society for Reproductive Medicine. Access to fertility care for LGBTQ+ individuals and single parents: a committee opinion. Fertil Steril. 2021;115(4):870-877.
10. Agrawal S, Kallen AN. Infertility disparities: a review of care access and outcomes. Curr Opin Obstet Gynecol. 2020;32(3):210-215.
11. Quinn GP, Sanchez JA, Sutton SK, et al. LGBTQ fertility and family building: a review of provider knowledge and attitudes. J Assist Reprod Genet. 2015;32(10):1507-1513.
12. Cwiak C, Edelman A, Ross L. Family planning access and non-traditional family building. Obstet Gynecol Clin North Am. 2019;46(4):711-724.
13. Agresti A, Min Y. Simple statistical methods for estimating relative risk in 2x2 contingency tables with paired data. Stat Med. 2005;24(5):729-740.
14. Lang TA, Altman DG. Statistical analyses and methods in the published literature: the SAMPL guidelines. Int J Nurs Stud. 2015;52(1):5-9.
